\documentclass[letterpaper]{recipe}
\usepackage[T1]{fontenc}
\usepackage[italian]{babel}
\usepackage{times,enumerate,ifthen}
\usepackage[usenames]{color}

\newcommand{\bsi}[2]{%
  \fontencoding{T1}\fontfamily{pbs}\fontseries{xl}\fontshape{n}%
  \fontsize{#1}{#2}\selectfont}

\renewcommand{\inghead}{\textbf{Ingredients}:\ }
%\renewcommand{\rechead}{\centering\bsi{24pt}{30pt}}
\renewcommand{\rechead}{\centering\huge\sffamily\bfseries\color{red}}
\makeatletter \setlength{\@totalleftmargin}{0pt}
\renewcommand*\l@subsubsection{\@dottedtocline{3}{3em}{0em}}
\makeatother \setlength\parindent{0pt} \setlength\parskip{2ex plus 0.5ex}
 \pagestyle{empty}
\begin{document}
\recipe{ Shrimp Feta Pasta } \ingred{3 tablespoons olive oil, 1 lb peeled and deveined shrimp,
5 cloves minced garlic (1 heaping tablespoon chopped garlic), 1 tablespoon white wine (Pinot Grigio),
1 lb linguine, 2 roma tomatoes, 2 teaspoon dried oregano, 1 teaspoon dried basil,
6 ounces crumbled feta cheese, 1 8-ounce can tomato sauce with garlic.
Parsley, garlic salt, and lemon juice to taste}

\begin{enumerate}[{\color{blue} 1.}]
\addtolength{\itemindent}{2em}
\item Boil water for pasta.  Add kosher salt and a pinch of olive oil.
\item Simmer shrimp, garlic, 2 tablespoons olive oil, and white wine in a medium skillet over medium heat for 5 minutes.
\item Take the core out of the tomatoes with a paring knife and cut a small X in the other end of the tomato.
\item When the water is boiling, drop the tomatoes in for 30 seconds, then immediately put them under running water to remove the skin.  Chop into medium-size pieces.
\item Put the linguine in the water for 8-10 minutes or until al-dente.
\item Remove the shrimp after 5 minutes and put in the tomatoes, tomato sauce, remaining 1 tablespoon olive oil, and herbs.  Simmer over medium heat for 10 minutes.
\item Toss hot pasta with shrimp, tomato sauce, and feta.  Feta will melt slightly.
\item Serve; finish with lemon juice to taste. 
\end{enumerate}
\end{document}
